Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
updated sec 6.1 and polished previous sec a bit more

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
mass ($M_{\rm cl}$),
size ($R$),
Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and 
gas surface density ($\Sigma_{\rm gas}$)
to examine their dynamics.

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:virial}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

@@

% PVE
We also compare the MCs identified in our simulations to 
those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of 
\Fig{alpha16}). The V-shaped dashed lines in the figure show the locii along which the given external pressures are needed for 
MCs to have linewidth for a given set of surface densities (see \Sec{PVE}).

The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures,
which are supported by turbulence and rotation. 
In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower, 
the MC itself is gravitationally unbound and is supported/confined 
by turbulence and rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.

The MCs in the satellite galaxies are found to have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\simeq$1.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
In addition, the MCs in the satellite galaxies follow the locus of 
$\log{(P/\textrm{K cm}^{-3})}$\eq6 (see bottom panel of \Fig{alpha16}). 
Given the low virial parameter and the $\sigma^2/R - \Sigma$ relation found for these MCs in the satellite galaxies, 
these structures are likely collapsing structures.
This paints a picture, in which \SF continues as gas from the satellite galaxies are being accreted onto the main galaxies during the EoR.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}
\caption{
Larson's relation of \flower across all snapshots (showing MC properties in different evolutionary
phases) and
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons16-28}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{alpha16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
where only denser substructures of the main disk of \flower are included.
\label{fig:alpha16-28-highncut}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}
\caption{
Same as \Fig{larsons16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
where only denser substructures of the main disk of \flower are included.
\label{fig:larsons16-28-highncut}}
\end{figure*}

@@

{\bf still yet to make the ``Q''-map}

@@

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more and less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
in closed box simulations; \citealt{}).
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to gunderstand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow.
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas

@@

\AP{This would be something like \quotes{origin of the cloud and implication of the found properties} if we put there toomre and CMF}
\DL{maybe just merge in the previous sections when we present the results?}

The largest molecular structure identified is essentially the main disk of \flower, which is ``broken'' down into smaller
spatial and mass structures that are also denser as we increase $n_{\rm cut}$. In any case,
the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
those observed in \z$\sim$2\,$-$\,4 galaxies with spatially resolved \obs.
The high pressure observed in \flower is also comparable to what has been observed in local ULIRGs; however, the 
molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are 
found throughout the disk. This difference likely stems from the different physical mechanisms giving rise 
to the formation (and thus the nature) of these molecular structures. 
For instance, in local ULIRGs, they are probably form by shock compression or cloud-cloud 
collision after the large amount of gas from the progenitor galaxy merger 
is being funneled toward the central region \citep{Tan00a, Wu18a},  % Tasker09a
whereas in \flower, which is actively accreting gaseous materials 
from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without 
funneling into the center).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed 
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{}).

\subsection{Virial Parameter}

\AP{I would move it to the previous section; I would use the virial parameter analysis to discuss the gravitational instability point more than on evolutionary state of the galaxy}

We quantify how stable a molecular structure is using the virial parameter, which
is defined using \Eq{virial} and describes the balance between kinetic and gravitational potential energies.
An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note that 
the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial} 
in \Sec{PVE})}.

The high $\alpha_{\rm vir}$ found in the majority of MCs of \flower suggest that they are not collapsing.
The largest structures are presumably supported by galactic rotation and turbulence from the feedback of
multiple episodes of \SF.
Turbulence in the smaller denser clouds are expected to cascade down over a timescale of $\sim$xxx\,Myr, after which the cloud will collapse
(its substructure likely collapses earlier than this timescale since turbulences would have dissipated).

While it may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
nature of the majority of the molecular gas in \flower and its SFR.
That is, if most of the molecular gas in \flower has high $\alpha_{\rm vir}$, why does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
This discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical MC hierarchy. These smaller structures likely no longer supported by large-scale gravitational potential and differential rotation,
and turbulence has dissipated rapidly on these scales to enable collapse \citep{Clark04a}.
Non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.
Note also that \citet{Pettitt18a} report that the virial parameter could be a poor indicator
for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. They
do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass
and the star formation efficiency ($M_*/M_{\rm cl}$).

@@

High resolution zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and is subject to the input model/sub-grid models adopted, 
provide an avenue to examine and postulate/make testable predictions on the morphology and dynamics of
the multi-phase ISM structures of the first galaxies and their satellite galaxies.
High resolution imaging of the molecular gas content in the first galaxies with ALMA and the Next Generation Very Large Array (ngVLA), on the other hand,
have the potential to provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.

>>>>

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as
mass ($M_{\rm cl}$),
size ($R$),
Mach number ($\mathcal{M}$), velocity dispersion ($\sigma$), and 
gas surface density ($\Sigma_{\rm gas}$)
to examine their dynamics.

@@

\subsection{Formalism: Virial Equilibrium and Larson's Relations}  \label{sec:PVE}
% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:alpha}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

We use the virial parameter, which is defined using \Eq{alpha} and describes 
the balance between kinetic and gravitational potential energies, 
to quantify how stable an MC is. 
An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that 
the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.

@@

% PVE
We also compare the MCs identified in our simulations to 
those observed in the Milky Way in the context of the $\sigma^2/R - \Sigma$ relation (see bottom panel of 
\Fig{alpha16}). The V-shaped dashed lines in the figure show the locii along which the given external pressures are needed for 
MCs to have linewidth for a given set of surface densities (see \Sec{PVE}). 
% (Rice+16) find variation in $V_0^2$, where they find larger linewidths for GMCs in inner galactic disk, but they find that the clouds in the Galactic disk are still consistent with SVE (see also Solomon87a ; cf. Heyer+09).

The lower $\alpha_{\rm vir}$ and $P_{\rm ext}$ compared to their parent MCs are consistent with
the conventional wisdom that collapsing structures result from local gravitational
instability within globally non-collapsing structures \citep[see e.g.,][]{Ballesteros-Paredes11a},
which are supported by turbulence and rotation. 
In fact, based on the virial parameter, velocity dispersion, and pressure of the MC identified in the main disk of \flower, 
the MC itself is gravitationally unbound and is supported/confined 
by turbulence (from the feedback of multiple episodes of \SF) 
and galactic rotation on large scales (occupying the high pressure region shown in the bottom panel of \Fig{alpha16}).
% Turbulence in these substructures further dissipates in % e.g., shocks on even smaller scales, allowing sub-MCs to be bound and collapse.

The MCs in the satellite galaxies are found to have
lower virial parameters compared to the (sub-)MCs in the main disk of \flower,
with $\alpha_{\rm vir}\approx$\,2.
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). 
In addition, the MCs in the satellite galaxies follow the locus of 
$\log{(P/\textrm{K cm}^{-3})}$\eq6 (see bottom panel of \Fig{alpha16}). 
Given the low virial parameter and the $\sigma^2/R - \Sigma$ relation found for these MCs in the satellite galaxies, 
these structures are likely collapsing structures.
This paints a picture, in which \SF continues as gas from the satellite galaxies are being accreted onto the main galaxies during the EoR.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}
\caption{
Comparison of the MCs of \flower identified across all snapshots over the course of 700\,Myr (star symbols)
to those observed in nearby and the \z$\sim$2 star-forming galaxy
in the context of the linewidth-size relation --- showing variations in their properties at 
the different evolutionary phases of \flower and with varying SFRs.
\label{fig:larsons16-28}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{alpha16-28}, but only the denser substructures of the main disk of \flower are included
(i.e., MCs here are identified with the highest $n_{\rm cut}$).
\label{fig:alpha16-28-highncut}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}
\caption{
Same as \Fig{larsons16-28}, but only the denser substructures of the main disk of \flower are included
(i.e., MCs here are identified with the highest $n_{\rm cut}$).
\label{fig:larsons16-28-highncut}}
\end{figure*}

@@

{\bf still yet to make the ``Q''-map} \\

We overplot the MCs on the Toomre-Q map.

@@

% a bit on caveat
One should, however, keep in mind that 
the slope of the CMF reported here is subject
to the uncertainties in the analysis method and the resolution of our simulation. 
That is, we are likely biased to finding more massive clouds due to resolution effects; 
it is possible that we may identify more and less massive MCs if our simulation 
was done at a higher resolution. 
That said, one must acknowledge that such a zoom-in simulation is currently too expensive to perform with 
existing computational power.
In any case, similarly massive molecular clouds have been reported in simulations done at higher resolution (i.e., 
in closed box simulations; \citealt{}).
It is therefore conceivable that our results are not that far off in spite of the limited resolution ($l\approx$30\,pc).
Future higher resolution zoom-in simulations would certainly be useful to understand
the evolving dynamical properties of the lower-mass molecular structures in
galaxies at EoR under the influence of gas inflow/outflow (i.e., accounting for energy injection at large scale due to infall/outflow).
% 
%On the contrary, an advantage of using cosmological zoom-in simulations for this study
%is that our computational boxes are not closed, allowing us to examine how
%the molecular complexes' properties vary under the influence of gas inflow/outflow 
%(see e.g., \citealt{Klessen10a, Goldbaum11a}). % turbulence when disk still accreting gas

@@

\subsection{Origin of the MCs} \label{sec:origin}
The largest molecular structure identified is essentially the main disk of \flower, which is ``broken'' down into smaller
spatial and mass structures that are also denser as we increase $n_{\rm cut}$. In any case,
the MCs we identified are much bigger in size and mass than nearby GMCs, which is consistent with
those observed in $z$\,\ssim2$-$4 galaxies based on spatially resolved imaging.

The high pressure observed in \flower is also comparable to what has been observed in local ULIRGs; however, the 
molecular clouds in the latter are concentrated within their central regions and have typical sizes of $\sim$70$-$100\,pc and masses on the order of $\sim$10$^9$\,\Msun
\citep{Downes98a, Sakamoto08a}. In our simulation, the high pressure MCs of \flower are 
found throughout the disk. This difference likely stems from the different physical mechanisms giving rise 
to the formation (and thus the nature) of these molecular structures. 
For instance, in local ULIRGs, they are probably form by shock compression or cloud-cloud 
collision after the large amount of gas from the progenitor galaxy merger 
is being funneled toward the central region \citep{Tan00a, Wu18a},  % Tasker09a
whereas in \flower, which is actively accreting gaseous materials 
from the surrounding, they are probably form from constant cold gas accretion onto the entire galaxy (without 
requiring gas to be funneled into the central region).
This latter mechanism may also be the dominant mode for forming the highly supersonic massive MCs observed 
in gas-rich star-forming galaxies at $z$\ssim2 (see also e.g., \citealt{}).
The constant inter-cloud collision as gas is being accreted onto the main galaxy would also render 
the MCs to be gravitationally unbound (see e.g., \citealt{Dobbs11a}), which would be consistent with/explain the 
high $\alpha_{\rm vir}$ found for the MCs in the main disk of \flower.

\subsection{Virial Parameter, Collapse, and high SFR at high-\z}

While it may appear that there is an inconsistency between the high $\alpha_{\rm vir}$
nature of the majority of the molecular gas in \flower and its SFR.
That is, if most of the molecular gas in \flower has high $\alpha_{\rm vir}$, why does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
This discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical MC hierarchy. These smaller structures are 
no longer supported by large-scale gravitational potential and differential rotation,
as turbulence has dissipated rapidly on these smaller scales to enable collapse \citep{Clark04a}.
In addition, non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation.
Note also that \citet{Pettitt18a} report that the virial parameter could be a poor indicator
for the star-forming capacity of the massive (10$^{5-6}$\,\Msun) ``clouds'' in their simulation. They
do not find any significant correlation between $\alpha_{\rm vir}$ and cloud mass
and the star formation efficiency ($M_*/M_{\rm cl}$).

@@

High resolution zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and is subject to the input model/sub-grid models adopted, 
provide an avenue to examine and postulate/make testable predictions on the morphology and dynamics of
the multi-phase ISM structures of the first galaxies and their satellite galaxies.
High resolution imaging of the molecular gas content in the first galaxies with ALMA and the ngVLA, on the other hand,
have the potential to provide useful observational data to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
